---
title: "Developing Data Products Course Project"
author: "Tim Bowler"
date: "May 18, 2017"
output: ioslides_presentation
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Iris Dataset K-means Example

This presentation is being created as part of the peer assessment for the Coursera Developing Data Products class.  The assignment's objective is to ensure the following concepts are reinforced:

- Build a data product application in shiny
- Develop a slide presentation in Rstudio Presenter or Slidify to pitch the application

## The Application

To demonstrate understanding of using **Shiny** to build an application, a simple application called **developing_data_products_project** has been deployed on [shinyapp.io](https://timbowler1.shinyapps.io/developing_data_products_project/)

The appication allows the user to:
- select the variable inputs to be used in constructing a k-means clustering graph
- select the number of clusters to plot

This application was developed and minimally tweaked by referring to the example at the Rstudio Shiny [Gallery](http://shiny.rstudio.com/gallery/)

## The Data

This application is based on the Iris dataset is the base R package.

This famous iris data set gives the measurements in centimeters of the variables sepal length and width and petal length and width, respectively, for 50 flowers from each of 3 species of iris. The species are Iris setosa, versicolor, and virginica.

Source code for the project is available on [GitHub](https://github.com/timbowler/DevDataProducts_Project)

## Data

```{r code, comment = "", echo = TRUE, eval = TRUE}
head(iris)
```
